---
title: "Analysis"
author: "Ashish"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: paper
---
Initialization
===
```{r, message=FALSE}
rm(list=ls())
library(rsurveyutils)
library(here)
library(lmerTest)
library(tidyverse)
library(ggthemr)
library(brms)
library(rsurveyutils)
library(sjPlot)
theme_set(theme_bw())
library(tidylog)
library(tidybayes)
```


Preprocessing
===


Read data
---
```{r, message=FALSE}
filepath <- "data/proc/micronarrative_llm_vs_qualtrics_aug2024_proc.csv"
df_raw <- read_csv(here(filepath))
```



Process data
---
```{r, message=FALSE}

df_raw$order %>% table

df_survey_bp <- df_raw %>% 
  mutate(start_date = ymd_hms(start_date),
         end_date = ymd_hms(end_date)) %>%
  arrange(start_date) %>% 
  mutate(first_activity = str_extract(order, "^chatbot|^qualtrics")) %>% 
  mutate(first_activity = case_when(
    first_activity == "chatbot" ~ "bot",
    first_activity == "qualtrics" ~ "form",
    TRUE ~ NA_character_
  )) 

df_survey_wp <- df_survey_bp %>% 
  group_by(order) %>%
  slice(1:118) %>% # make group sizes equal
  ungroup 
```

```{r}

```



```{r, echo=FALSE}
# ------ End Preprocessing ------ #
# ----- Run all chunks above -----#
```



Preliminaries
===
```{r}
df_survey_bp$order %>% table
df_survey$order %>% table
```

Demographics
---
```{r}
df_survey_bp %>% 
  summarize(
    n = n(),
    mean_age = mean(age, na.rm=T),
    sd_age = sd(age, na.rm=T),
    min_age = min(age, na.rm=T),
    max_age = max(age, na.rm=T),
    n_18 = sum(age == 18, na.rm=T),
    pr_18 = mean(age == 18, na.rm=T),
    n_19 = sum(age == 19, na.rm=T),
    pr_19 = mean(age == 19, na.rm=T),
    n_20 = sum(age == 20, na.rm=T),
    pr_20 = mean(age == 20, na.rm=T),
    n_men = sum(gender == "Male", na.rm=T),
    n_women = sum(gender == "Female", na.rm=T),
    n_other = sum(gender == "Other", na.rm=T)
  ) %>% 
  pivot_longer(everything()) %>% 
  as.data.frame

df_survey_bp %>% 
  select(starts_with("race"), -ends_with("TEXT")) %>% 
  pivot_longer(everything()) %>% 
  drop_na(value) %>% 
  count(value) %>% 
  arrange(desc(n)) %>% 
  mutate(pr = n/nrow(df_survey_bp)) %>% 
  as.data.frame()
# asian 
37+23+8+7+1+1
# other

```



Zero-order corr bot
---
```{r}
d <- df_survey_bp %>% 
  select(
    helpArticulate_bot, difficult_bot,
    feelingChange_bot, valuable_bot, 
    acc_obj_bot, acc_feel_bot,
    otherUnderstand_bot,
    privacy_bot, recommend_bot
  )


d %>% 
  cor_matrix_kbl(expand.grid(names(d), names(d)))
```

Zero-order corr form
---
```{r}
d <- df_survey_bp %>% 
  select(
    helpArticulate_form, difficult_form,
    feelingChange_form, valuable_form, 
    acc_obj_form, acc_feel_form,
    otherUnderstand_form,
    privacy_form, recommend_form
  )


d %>% 
  cor_matrix_kbl(expand.grid(names(d), names(d)))
```



Helpful in articulating
===

lmer
---
```{r}

d <- df_survey_wp %>% 
  select(pid, order, helpArticulate_bot, helpArticulate_form) %>% 
  pivot_longer(cols = -c(pid, order), 
               names_pattern = "helpArticulate_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = value/100)

hist(d$value)

d %>% 
  ggplot(aes(x = method, y = value)) +
  geom_point(position=position_jitter(.05), alpha=.3) +
  stat_summary(fun.data = "mean_cl_boot", color="darkred")

d %>% 
  lmer(value ~ method + (1|pid) + (method||order), data = .) %>%
  tab_model()
```
> chatbot more helpful

ZOIB within
---
```{r}
d <- df_survey_wp %>% 
  select(pid, order, helpArticulate_bot, helpArticulate_form) %>% 
  pivot_longer(cols = -c(pid, order), 
               names_pattern = "helpArticulate_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = value/100)

# f <- bf(
#   value_sc ~ method + (1|pid) + (1|order),
#   coi ~ method + (1|pid) + (1|order),
#   zoi ~ method + (1|pid) + (1|order),
#   phi ~ method + (1|pid) + (1|order)
# )
f <- bf(
  value_sc ~ method + (1|pid),
  coi ~ method + (1|pid),
  zoi ~ method + (1|pid),
  phi ~ method + (1|pid)
)

fit_articulate_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      control = list(adapt_delta = .90),
      file = "models/fit_articulate_zoib.rds",
      file_refit = "on_change"
  )
pp_check(fit_articulate_zoib)
summary(fit_articulate_zoib)

mu_intercept <- as_draws_df(fit_articulate_zoib)$b_Intercept 
mu_method <- as_draws_df(fit_articulate_zoib)$b_methodform
coi_intercept <- as_draws_df(fit_articulate_zoib)$b_coi_Intercept
coi_method <- as_draws_df(fit_articulate_zoib)$b_coi_methodform
phi_intercept <- as_draws_df(fit_articulate_zoib)$b_phi_Intercept
phi_method <- as_draws_df(fit_articulate_zoib)$b_phi_methodform
zoi_intercept <- as_draws_df(fit_articulate_zoib)$b_zoi_Intercept
zoi_method <- as_draws_df(fit_articulate_zoib)$b_zoi_methodform

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) < 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) < 0"
)
hypothesis(fit_articulate_zoib, h, alpha = .05)
hypothesis(fit_articulate_zoib, h, alpha = .10)

```


ZOIB between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, helpArticulate_bot, helpArticulate_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "helpArticulate_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100)

f <- bf(
  value_sc ~ method,
  coi ~ method,
  zoi ~ method,
  phi ~ method
)

fit_articulate_bp_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      # control = list(adapt_delta = .90),
      file = "models/fit_articulate_zoib_between.rds",
      file_refit = "on_change"
  )
pp_check(fit_articulate_bp_zoib)
summary(fit_articulate_bp_zoib)

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) < 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) < 0"
)
hypothesis(fit_articulate_bp_zoib, h, alpha = .05)
hypothesis(fit_articulate_bp_zoib, h, alpha = .10)
```

Beta between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, helpArticulate_bot, helpArticulate_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "helpArticulate_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100) %>% 
  mutate(value_sc = case_when(
    value_sc == 0 ~ 0.01,
    value_sc == 1 ~ 0.99,
    TRUE ~ value_sc
  )) %>% 
  mutate(method = factor(method, levels = c("form", "bot"))) 

f <- bf(
  value_sc ~ method,
  phi ~ method

)

fit_articulate_bp_beta <- d %>% 
  brm(f,
      data = .,
      family = Beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_articulate_beta_between.rds",
      file_refit = "on_change"
  )


pp_check(fit_articulate_bp_beta)
summary(fit_articulate_bp_beta)

h <- c(
  "mu" = "plogis(Intercept + methodbot) - plogis(Intercept) > 0"
)
hypothesis(fit_articulate_bp_beta, h, alpha = .05)
hypothesis(fit_articulate_bp_beta, h, alpha = .10)

```



Bayesian Gaussian
---
```{r}
d <- df_survey_wp %>% 
  select(pid, helpArticulate_bot, helpArticulate_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "helpArticulate_(.*)", 
               names_to = "method",
               values_to = "value")

fit_articulate_gaussian <- d %>%
  brm(value ~ method + (1|pid),
      data = .,
      family = gaussian(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_articulate_gaussian.rds",
      file_refit = "on_change"
  )

pp_check(fit_articulate_gaussian)
summary(fit_articulate_gaussian)

```



Difficult to respond
===

lmer
---
```{r}
d <- df_survey_wp %>% 
  select(pid, difficult_bot, difficult_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "difficult_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = value/100)
hist(d$value)

d %>% 
  ggplot(aes(x = method, y = value)) +
  geom_point(position=position_jitter(.05), alpha=.3) +
  stat_summary(fun.data = "mean_cl_boot", color="darkred")

d %>% 
  lmer(value ~ method + (1|method), data = .) %>%
  tab_model()
```
> no effect.

Bayesian ZOIB
---
```{r}

d <- df_survey_wp %>% 
  select(pid, order, difficult_bot, difficult_form) %>% 
  pivot_longer(cols = -c(pid, order),
               names_pattern = "difficult_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = value/100)

# f <- bf(
#   value_sc ~ method + (1|pid) + (method|order),
#   coi ~ method + (1|pid) + (method|order),
#   zoi ~ method + (1|pid) + (method|order),
#   phi ~ method + (1|pid) + (method|order)
# )
f <- bf(
  value_sc ~ method + (1|pid),
  coi ~ method + (1|pid),
  zoi ~ method + (1|pid),
  phi ~ method + (1|pid)
)

fit_difficult_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      control = list(adapt_delta = .99),
      file = "models/fit_difficult_zoib.rds",
      file_refit = "on_change"
  )

pp_check(fit_difficult_zoib)
summary(fit_difficult_zoib)


conditional_effects(fit_difficult_zoib)


mu_intercept <- as_draws_df(fit_difficult_zoib)$b_Intercept 
mu_method <- as_draws_df(fit_difficult_zoib)$b_methodform
coi_intercept <- as_draws_df(fit_difficult_zoib)$b_coi_Intercept
coi_method <- as_draws_df(fit_difficult_zoib)$b_coi_methodform
phi_intercept <- as_draws_df(fit_difficult_zoib)$b_phi_Intercept
phi_method <- as_draws_df(fit_difficult_zoib)$b_phi_methodform
zoi_intercept <- as_draws_df(fit_difficult_zoib)$b_zoi_Intercept
zoi_method <- as_draws_df(fit_difficult_zoib)$b_zoi_methodform

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) > 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) > 0"
)
hypothesis(fit_difficult_zoib, h, alpha = .05)
hypothesis(fit_difficult_zoib, h, alpha = .10)

```




ZOIB between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, difficult_bot, difficult_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "difficult_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100)


f <- bf(
  value_sc ~ method,
  coi ~ method,
  zoi ~ method,
  phi ~ method
)

fit_difficult_bp_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      # control = list(adapt_delta = .90),
      file = "models/fit_difficult_zoib_between.rds",
      file_refit = "on_change"
  )

conditional_effects(fit_difficult_bp_zoib)
pp_check(fit_difficult_bp_zoib)
summary(fit_difficult_bp_zoib)

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) > 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) > 0"
)

hypothesis(fit_difficult_bp_zoib, h, alpha = .05)
hypothesis(fit_difficult_bp_zoib, h, alpha = .10)

```

Beta between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, difficult_bot, difficult_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "difficult_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100) %>% 
  mutate(value_sc = case_when(
    value_sc == 0 ~ 0.01,
    value_sc == 1 ~ 0.99,
    TRUE ~ value_sc
  ))  %>% 
  mutate(method = factor(method, levels = c("form", "bot"))) 

f <- bf(
  value_sc ~ method,
  phi ~ method
)

fit_difficult_bp_beta <- d %>% 
  brm(f,
      data = .,
      family = Beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_difficult_beta_between.rds",
      file_refit = "on_change"
  )

pp_check(fit_difficult_bp_beta)


h <- c(
  "mu" = "plogis(Intercept + methodbot) - plogis(Intercept) < 0"
)
hypothesis(fit_difficult_bp_beta, h, alpha = .05)
hypothesis(fit_difficult_bp_beta, h, alpha = .10)

```


Bayesian gaussian
---
```{r}
d <- df_survey_wp %>% 
  select(pid, difficult_bot, difficult_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "difficult_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = value/100)

fit_difficult_gaussian <- d %>%
  brm(value ~ method + (1|pid),
      data = .,
      family = gaussian(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_difficult_gaussian.rds",
      file_refit = "on_change"
  )

pp_check(fit_difficult_gaussian)
summary(fit_difficult_gaussian)


```



Valuable for youth
===

lmer
---
```{r}
d <- df_survey_wp %>% 
  select(pid, valuable_bot, valuable_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "valuable_(.*)", 
               names_to = "method",
               values_to = "value")  %>% 
  mutate(value_sc = value/100)
hist(d$value)

d %>% 
  ggplot(aes(x = method, y = value)) +
  geom_point(position=position_jitter(.05)) +
  stat_summary(fun.data = "mean_cl_boot")

d %>% 
  lmer(value ~ method + (1|method), data = .) %>%
  tab_model()
```
> form less valuable


Bayesian ZOIB
---
```{r}
d <- df_survey_wp %>% 
  select(pid, order, valuable_bot, valuable_form) %>% 
  pivot_longer(cols = -c(pid, order),
               names_pattern = "valuable_(.*)", 
               names_to = "method",
               values_to = "value")  %>% 
  mutate(value_sc = value/100)



# f <- bf(
#   value_sc ~ method + (1|pid) + (method|order),
#   coi ~ method + (1|pid) + (method|order),
#   zoi ~ method + (1|pid) + (method|order),
#   phi ~ method + (1|pid) + (method|order)
# )
f <- bf(
  value_sc ~ method + (1|pid),
  coi ~ method + (1|pid),
  zoi ~ method + (1|pid),
  phi ~ method + (1|pid)
)

fit_valuable_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      control = list(adapt_delta = .90),
      file = "models/fit_valuable_zoib.rds",
      file_refit = "on_change"
  )

pp_check(fit_valuable_zoib)
summary(fit_valuable_zoib)


conditional_effects(fit_valuable_zoib)


mu_intercept <- as_draws_df(fit_valuable_zoib)$b_Intercept 
mu_method <- as_draws_df(fit_valuable_zoib)$b_methodform
coi_intercept <- as_draws_df(fit_valuable_zoib)$b_coi_Intercept
coi_method <- as_draws_df(fit_valuable_zoib)$b_coi_methodform
phi_intercept <- as_draws_df(fit_valuable_zoib)$b_phi_Intercept
phi_method <- as_draws_df(fit_valuable_zoib)$b_phi_methodform
zoi_intercept <- as_draws_df(fit_valuable_zoib)$b_zoi_Intercept
zoi_method <- as_draws_df(fit_valuable_zoib)$b_zoi_methodform

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) < 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) < 0"
)
hypothesis(fit_valuable_zoib, h, alpha = .05)
hypothesis(fit_valuable_zoib, h, alpha = .10)
```


ZOIB between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, valuable_bot, valuable_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "valuable_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100)

f <- bf(
  value_sc ~ method,
  coi ~ method,
  zoi ~ method,
  phi ~ method
)

fit_valuable_bp_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      # control = list(adapt_delta = .90),
      file = "models/fit_valuable_zoib_between.rds",
      file_refit = "on_change"
  )

pp_check(fit_valuable_bp_zoib)
summary(fit_valuable_bp_zoib)

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) = 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) = 0",
  "phi" = "plogis(phi_Intercept + phi_methodform) - plogis(phi_Intercept) = 0",
  "zoi" = "plogis(zoi_Intercept + zoi_methodform) - plogis(zoi_Intercept) = 0"
)

hypothesis(fit_valuable_bp_zoib, h, alpha = .05)
hypothesis(fit_valuable_bp_zoib, h, alpha = .10)


```

Beta between
----
```{r}

d <- df_survey_bp %>% 
  select(pid, first_activity, valuable_bot, valuable_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "valuable_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100) %>% 
  mutate(value_sc = case_when(
    value_sc == 0 ~ 0.01,
    value_sc == 1 ~ 0.99,
    TRUE ~ value_sc
  )) %>% 
  mutate(method = factor(method, levels = c("form", "bot"))) 


f <- bf(
  value_sc ~ method,
  phi ~ method
)

fit_valuable_bp_beta <- d %>% 
  brm(f,
      data = .,
      family = Beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_valuable_beta_between.rds",
      file_refit = "on_change"
  )
pp_check(fit_valuable_bp_beta)
summary(fit_valuable_bp_beta)


h <- c(
  "mu" = "plogis(Intercept + methodbot) - plogis(Intercept) > 0"
)
hypothesis(fit_valuable_bp_beta, h, alpha = .05)
hypothesis(fit_valuable_bp_beta, h, alpha = .10)

```


Bayesian gaussian
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, valuable_bot, valuable_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "valuable_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100)

fit_valuable_zoib_gaussian <- d %>% 
  brm(value ~ method + (1|pid),
      data = .,
      family = gaussian(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_valuable_gaussian.rds",
      file_refit = "on_change"
  )
pp_check(fit_valuable_zoib_gaussian)
summary(fit_valuable_zoib_gaussian)

```

Feeling change
===

lmer
---
```{r}
d <- df_survey_wp %>% 
  select(pid, feelingChange_bot, feelingChange_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "feelingChange_(.*)", 
               names_to = "method",
               values_to = "value") 
hist(d$value)

d %>% 
  ggplot(aes(x = method, y = value)) +
  geom_point(position=position_jitter(.05), alpha = .3)  +
  stat_summary(fun.data = "mean_cl_boot", color="darkred")

d %>% 
  lmer(value ~ method + (1|method), data = .) %>%
  tab_model()
```
> not really a difference between the two and neither are that helpful

Bayesian ZOIB
---

### Diff between methods
```{r}

d <- df_survey_wp %>% 
  select(pid, order, feelingChange_bot, feelingChange_form) %>% 
  pivot_longer(cols = -c(pid, order),
               names_pattern = "feelingChange_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = (value+100)/200)



# f <- bf(
#   value_sc ~ method + (1|pid) + (method|order),
#   coi ~ method + (1|pid) + (method|order),
#   zoi ~ method + (1|pid) + (method|order),
#   phi ~ method + (1|pid) + (method|order)
# )
f <- bf(
  value_sc ~ method + (1|pid),
  coi ~ method + (1|pid),
  zoi ~ method + (1|pid),
  phi ~ method + (1|pid)
)


fit_feelingChange_zoib <- d %>%
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      control = list(adapt_delta = .90),
      file = "models/fit_feelingChange_zoib.rds",
      file_refit = "on_change"
  )

pp_check(fit_feelingChange_zoib)
summary(fit_feelingChange_zoib)

conditional_effects(fit_feelingChange_zoib)


mu_intercept <- as_draws_df(fit_feelingChange_zoib)$b_Intercept 
mu_method <- as_draws_df(fit_feelingChange_zoib)$b_methodform
coi_intercept <- as_draws_df(fit_feelingChange_zoib)$b_coi_Intercept
coi_method <- as_draws_df(fit_feelingChange_zoib)$b_coi_methodform
phi_intercept <- as_draws_df(fit_feelingChange_zoib)$b_phi_Intercept
phi_method <- as_draws_df(fit_feelingChange_zoib)$b_phi_methodform
zoi_intercept <- as_draws_df(fit_feelingChange_zoib)$b_zoi_Intercept
zoi_method <- as_draws_df(fit_feelingChange_zoib)$b_zoi_methodform

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) < 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) < 0"
)
hypothesis(fit_feelingChange_zoib, h, alpha = .05)
hypothesis(fit_feelingChange_zoib, h, alpha = .10)

```
> Nope (is something wrong here?)

### Diff from no change
```{r}

```

ZOIB between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, feelingChange_bot, feelingChange_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "feelingChange_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = (value+100)/200)

f <- bf(
  value_sc ~ method,
  coi ~ method,
  zoi ~ method,
  phi ~ method
)

fit_feelingChange_bp_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      # control = list(adapt_delta = .90),
      file = "models/fit_feelingChange_zoib_between.rds",
      file_refit = "on_change"
  )
h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) = 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) = 0",
  "phi" = "plogis(phi_Intercept + phi_methodform) - plogis(phi_Intercept) = 0",
  "zoi" = "plogis(zoi_Intercept + zoi_methodform) - plogis(zoi_Intercept) = 0"
)
hypothesis(fit_feelingChange_bp_zoib, h, alpha = .05)
hypothesis(fit_feelingChange_bp_zoib, h, alpha = .10)

```

Beta between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, feelingChange_bot, feelingChange_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "feelingChange_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = (value+100)/200) %>% 
  mutate(value_sc = case_when(
    value_sc == 0 ~ 0.01,
    value_sc == 1 ~ 0.99,
    TRUE ~ value_sc
  )) %>% 
  mutate(method = factor(method, levels = c("bot", "form")))

f <- bf(
  value_sc ~ method,
  phi ~ method
)

fit_feelingChange_bp_beta <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_feelingChange_beta_between.rds",
      file_refit = "on_change"
  )

pp_check(fit_feelingChange_bp_beta)
summary(fit_feelingChange_bp_beta)

h <- c(
  "mu" = "plogis(Intercept + methodbot) - plogis(Intercept) > 0"
)
hypothesis(fit_feelingChange_bp_beta, h, alpha = .05)
hypothesis(fit_feelingChange_bp_beta, h, alpha = .10)

```



Bayesian Gaussian
---
```{r}
d <- df_survey_wp %>% 
  select(pid, feelingChange_bot, feelingChange_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "feelingChange_(.*)", 
               names_to = "method",
               values_to = "value") 

fit_feelingChange_gaussian <- d %>%
  brm(value ~ method + (1|pid),
      data = .,
      family = gaussian(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_feelingChange_gaussian.rds",
      file_refit = "on_change"
  )

pp_check(fit_feelingChange_gaussian)
summary(fit_feelingChange_gaussian)



```


Accurate objective circumstances
===

lmer
---
```{r}
d <- df_survey_wp %>% 
  select(pid, acc_obj_bot, acc_obj_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "acc_obj_(.*)", 
               names_to = "method",
               values_to = "value") 
hist(d$value)

d %>% 
  ggplot(aes(x = method, y = value)) +
  geom_point(position=position_jitter(.05)) +
  stat_summary(fun.data = "mean_cl_boot")

d %>% 
  lmer(value ~ method + (1|method), data = .) %>%
  tab_model()
```
> no diff


Bayesian ZOIB
---
```{r}
d <- df_survey_wp %>% 
  select(pid, order, acc_obj_bot, acc_obj_form) %>% 
  pivot_longer(cols = -c(pid, order),
               names_pattern = "acc_obj_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = value/100)


# f <- bf(
#   value_sc ~ method + (1|pid) + (method|order),
#   coi ~ method + (1|pid) + (method|order),
#   zoi ~ method + (1|pid) + (method|order),
#   phi ~ method + (1|pid) + (method|order)
# )
f <- bf(
  value_sc ~ method + (1|pid),
  coi ~ method + (1|pid),
  zoi ~ method + (1|pid),
  phi ~ method + (1|pid)
)

fit_acc_obj_zoib <- d %>%
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      control = list(adapt_delta = .90),
      file = "models/fit_acc_obj_zoib.rds",
      file_refit = "on_change"
  )
pp_check(fit_acc_obj_zoib)
summary(fit_acc_obj_zoib)

conditional_effects(fit_acc_obj_zoib)


mu_intercept <- as_draws_df(fit_acc_obj_zoib)$b_Intercept 
mu_method <- as_draws_df(fit_acc_obj_zoib)$b_methodform
coi_intercept <- as_draws_df(fit_acc_obj_zoib)$b_coi_Intercept
coi_method <- as_draws_df(fit_acc_obj_zoib)$b_coi_methodform
phi_intercept <- as_draws_df(fit_acc_obj_zoib)$b_phi_Intercept
phi_method <- as_draws_df(fit_acc_obj_zoib)$b_phi_methodform
zoi_intercept <- as_draws_df(fit_acc_obj_zoib)$b_zoi_Intercept
zoi_method <- as_draws_df(fit_acc_obj_zoib)$b_zoi_methodform

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) < 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) < 0"
)
hypothesis(fit_acc_obj_zoib, h, alpha = .05)
hypothesis(fit_acc_obj_zoib, h, alpha = .10)
```
> mu yes, coi no

ZOIB between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, acc_obj_bot, acc_obj_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "acc_obj_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100)

f <- bf(
  value_sc ~ method,
  coi ~ method,
  zoi ~ method,
  phi ~ method
)

fit_acc_obj_bp_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      # control = list(adapt_delta = .90),
      file = "models/fit_acc_obj_zoib_between.rds",
      file_refit = "on_change"
  )
h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) = 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) = 0",
  "phi" = "plogis(phi_Intercept + phi_methodform) - plogis(phi_Intercept) = 0",
  "zoi" = "plogis(zoi_Intercept + zoi_methodform) - plogis(zoi_Intercept) = 0"
)
hypothesis(fit_acc_obj_bp_zoib, h, alpha = .05)
hypothesis(fit_acc_obj_bp_zoib, h, alpha = .10)


```

Beta between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, acc_obj_bot, acc_obj_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "acc_obj_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100) %>% 
  mutate(value_sc = case_when(
    value_sc == 0 ~ 0.01,
    value_sc == 1 ~ 0.99,
    TRUE ~ value_sc
  )) %>% 
  mutate(method = factor(method, levels = c("form", "bot"))) 

f <- bf(
  value_sc ~ method,
  phi ~ method
)

fit_acc_obj_bp_beta <- d %>% 
  brm(f,
      data = .,
      family = Beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_acc_obj_beta_between.rds",
      file_refit = "on_change"
  )

pp_check(fit_acc_obj_bp_beta)
summary(fit_acc_obj_bp_beta)

h <- c(
  "mu" = "plogis(Intercept + methodbot) - plogis(Intercept) > 0"
)
hypothesis(fit_acc_obj_bp_beta, h, alpha = .05)
hypothesis(fit_acc_obj_bp_beta, h, alpha = .10)

```



Bayesian gaussian
---
```{r}
d <- df_survey_wp %>% 
  select(pid, acc_obj_bot, acc_obj_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "acc_obj_(.*)", 
               names_to = "method",
               values_to = "value")
hist(d$value)

fit_acc_obj_gaussian <- d %>%
  brm(value ~ method + (1|pid),
      data = .,
      family = gaussian(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_acc_obj_gaussian.rds",
      file_refit = "on_change"
  )

pp_check(fit_acc_obj_gaussian)
summary(fit_acc_obj_gaussian)

```


Accurate feelings
===

lmer
---
```{r}
d <- df_survey_wp %>% 
  select(pid, acc_feel_bot, acc_feel_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "acc_feel_(.*)", 
               names_to = "method",
               values_to = "value") 

d %>% 
  ggplot(aes(x = method, y = value)) +
  geom_point(position=position_jitter(.05)) +
  stat_summary(fun.data = "mean_cl_boot")

d %>% 
  lmer(value ~ method + (1|method), data = .) %>%
  tab_model()
```
> no diff

Bayesian ZOIB
---
```{r}
d <- df_survey_wp %>% 
  select(pid, order, acc_feel_bot, acc_feel_form) %>% 
  pivot_longer(cols = -c(pid, order),
               names_pattern = "acc_feel_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = value/100)


# f <- bf(
#   value_sc ~ method + (1|pid) + (method|order),
#   coi ~ method + (1|pid) + (method|order),
#   zoi ~ method + (1|pid) + (method|order),
#   phi ~ method + (1|pid) + (method|order)
# )
f <- bf(
  value_sc ~ method + (1|pid),
  coi ~ method + (1|pid),
  zoi ~ method + (1|pid),
  phi ~ method + (1|pid)
)

fit_acc_feel_zoib <- d %>%
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      control = list(adapt_delta = .90),
      file = "models/fit_acc_feel_zoib.rds",
      file_refit = "on_change"
  )
pp_check(fit_acc_feel_zoib)
summary(fit_acc_feel_zoib)


conditional_effects(fit_acc_feel_zoib)


mu_intercept <- as_draws_df(fit_acc_feel_zoib)$b_Intercept 
mu_method <- as_draws_df(fit_acc_feel_zoib)$b_methodform
coi_intercept <- as_draws_df(fit_acc_feel_zoib)$b_coi_Intercept
coi_method <- as_draws_df(fit_acc_feel_zoib)$b_coi_methodform
phi_intercept <- as_draws_df(fit_acc_feel_zoib)$b_phi_Intercept
phi_method <- as_draws_df(fit_acc_feel_zoib)$b_phi_methodform
zoi_intercept <- as_draws_df(fit_acc_feel_zoib)$b_zoi_Intercept
zoi_method <- as_draws_df(fit_acc_feel_zoib)$b_zoi_methodform

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) < 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) < 0"
)
hypothesis(fit_acc_feel_zoib, h, alpha = .05)
hypothesis(fit_acc_feel_zoib, h, alpha = .10)

```
> mu yes, coi no


ZOIB between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, acc_feel_bot, acc_feel_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "acc_feel_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100)

f <- bf(
  value_sc ~ method,
  coi ~ method,
  zoi ~ method,
  phi ~ method
)

fit_acc_feel_bp_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      # control = list(adapt_delta = .90),
      file = "models/fit_acc_feel_zoib_between.rds",
      file_refit = "on_change"
  )

pp_check(fit_acc_feel_bp_zoib)
summary(fit_acc_feel_bp_zoib)

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) = 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) = 0",
  "phi" = "plogis(phi_Intercept + phi_methodform) - plogis(phi_Intercept) = 0",
  "zoi" = "plogis(zoi_Intercept + zoi_methodform) - plogis(zoi_Intercept) = 0"
)

hypothesis(fit_acc_feel_bp_zoib, h, alpha = .05)
hypothesis(fit_acc_feel_bp_zoib, h, alpha = .10)

```

Beta between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, acc_feel_bot, acc_feel_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "acc_feel_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100) %>% 
  mutate(value_sc = case_when(
    value_sc == 0 ~ 0.01,
    value_sc == 1 ~ 0.99,
    TRUE ~ value_sc
  )) %>% 
  mutate(method = factor(method, levels = c("form", "bot"))) 

f <- bf(
  value_sc ~ method,
  phi ~ method
)

fit_acc_feel_bp_beta <- d %>% 
  brm(f,
      data = .,
      family = Beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_acc_feel_beta_between.rds",
      file_refit = "on_change"
  )

pp_check(fit_acc_feel_bp_beta)
summary(fit_acc_feel_bp_beta)


h <- c(
  "mu" = "plogis(Intercept + methodbot) - plogis(Intercept) > 0"
)
hypothesis(fit_acc_feel_bp_beta, h, alpha = .05)
hypothesis(fit_acc_feel_bp_beta, h, alpha = .10)

```


Bayesian gaussian
---
```{r}

d <- df_survey_wp %>% 
  select(pid, acc_feel_bot, acc_feel_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "acc_feel_(.*)", 
               names_to = "method",
               values_to = "value")

hist(d$value)

fit_acc_feel_gaussian <- d %>%
  brm(value ~ method + (1|pid),
      data = .,
      family = gaussian(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_acc_feel_gaussian.rds",
      file_refit = "on_change"
  )

pp_check(fit_acc_feel_gaussian)
summary(fit_acc_feel_gaussian)


```


Others would understand
===

lmer
---
```{r}
d <- df_survey_wp %>% 
  select(pid, otherUnderstand_bot, otherUnderstand_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "otherUnderstand_(.*)", 
               names_to = "method",
               values_to = "value") 

d %>% 
  ggplot(aes(x = method, y = value)) +
  geom_point(position=position_jitter(.05)) +
  stat_summary(fun.data = "mean_cl_boot")
d %>% 
  ggplot(aes(x = method, y = value)) +
  # geom_point(position=position_jitter(.05)) +
  stat_summary(fun.data = "mean_cl_boot")

d %>% 
  lmer(value ~ method + (1|method), data = .) %>%
  tab_model()
```
> no diff and non convergence.


Bayesian ZOIB
---
```{r}
d <- df_survey_wp %>% 
  select(pid, order, otherUnderstand_bot, otherUnderstand_form) %>% 
  pivot_longer(cols = -c(pid, order),
               names_pattern = "otherUnderstand_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = value/100)


# f <- bf(
#   value_sc ~ method + (1|pid) + (method|order),
#   coi ~ method + (1|pid) + (method|order),
#   zoi ~ method + (1|pid) + (method|order),
#   phi ~ method + (1|pid) + (method|order)
# )
f <- bf(
  value_sc ~ method + (1|pid),
  coi ~ method + (1|pid),
  zoi ~ method + (1|pid),
  phi ~ method + (1|pid)
)


fit_otherUnderstand_zoib <- d %>%
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      control = list(adapt_delta = .90),
      file = "models/fit_otherUnderstand_zoib.rds",
      file_refit = "on_change"
  )

pp_check(fit_otherUnderstand_zoib)
summary(fit_otherUnderstand_zoib)


conditional_effects(fit_otherUnderstand_zoib)


mu_intercept <- as_draws_df(fit_otherUnderstand_zoib)$b_Intercept 
mu_method <- as_draws_df(fit_otherUnderstand_zoib)$b_methodform
coi_intercept <- as_draws_df(fit_otherUnderstand_zoib)$b_coi_Intercept
coi_method <- as_draws_df(fit_otherUnderstand_zoib)$b_coi_methodform
phi_intercept <- as_draws_df(fit_otherUnderstand_zoib)$b_phi_Intercept
phi_method <- as_draws_df(fit_otherUnderstand_zoib)$b_phi_methodform
zoi_intercept <- as_draws_df(fit_otherUnderstand_zoib)$b_zoi_Intercept
zoi_method <- as_draws_df(fit_otherUnderstand_zoib)$b_zoi_methodform

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) < 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) < 0"
)
hypothesis(fit_otherUnderstand_zoib, h, alpha = .05)
hypothesis(fit_otherUnderstand_zoib, h, alpha = .10)

```
> mu yes, coi no


ZOIB between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, otherUnderstand_bot, otherUnderstand_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "otherUnderstand_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100)

f <- bf(
  value_sc ~ method,
  coi ~ method,
  zoi ~ method,
  phi ~ method
)

fit_otherUnderstand_bp_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      # control = list(adapt_delta = .90),
      file = "models/fit_otherUnderstand_zoib_between.rds",
      file_refit = "on_change"
  )

pp_check(fit_otherUnderstand_bp_zoib)
summary(fit_otherUnderstand_bp_zoib)

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) = 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) = 0",
  "phi" = "plogis(phi_Intercept + phi_methodform) - plogis(phi_Intercept) = 0",
  "zoi" = "plogis(zoi_Intercept + zoi_methodform) - plogis(zoi_Intercept) = 0"
)

hypothesis(fit_otherUnderstand_bp_zoib, h, alpha = .05)
hypothesis(fit_otherUnderstand_bp_zoib, h, alpha = .10)
```

Beta between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, otherUnderstand_bot, otherUnderstand_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "otherUnderstand_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100) %>% 
  mutate(value_sc = case_when(
    value_sc == 0 ~ 0.01,
    value_sc == 1 ~ 0.99,
    TRUE ~ value_sc
  )) %>% 
  mutate(method = factor(method, levels = c("form", "bot"))) 

f <- bf(
  value_sc ~ method,
  phi ~ method
)

fit_otherUnderstand_bp_beta <- d %>% 
  brm(f,
      data = .,
      family = Beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_otherUnderstand_beta_between.rds",
      file_refit = "on_change"
  )

pp_check(fit_otherUnderstand_bp_beta)
summary(fit_otherUnderstand_bp_beta)

h <- c(
  "mu" = "plogis(Intercept + methodbot) - plogis(Intercept) > 0"
)
hypothesis(fit_otherUnderstand_bp_beta, h, alpha = .05)
hypothesis(fit_otherUnderstand_bp_beta, h, alpha = .10)



```


Bayesian gaussian
---
```{r}
d <- df_survey_wp %>% 
  select(pid, otherUnderstand_bot, otherUnderstand_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "otherUnderstand_(.*)", 
               names_to = "method",
               values_to = "value")

fit_otherUnderstand_gaussian <- d %>%
  brm(value ~ method + (1|pid),
      data = .,
      family = gaussian(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_otherUnderstand_gaussian.rds",
      file_refit = "on_change"
  )

pp_check(fit_otherUnderstand_gaussian)
summary(fit_otherUnderstand_gaussian)
```


Privacy concerns
===

lmer
---
```{r}
d <- df_survey_wp %>% 
  select(pid, privacy_bot, privacy_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "privacy_(.*)", 
               names_to = "method",
               values_to = "value") 

d %>% 
  ggplot(aes(x = method, y = value)) +
  geom_point(position=position_jitter(.05)) +
  stat_summary(fun.data = "mean_cl_boot")

d %>% 
  lmer(value ~ method + (1|method), data = .) %>%
  tab_model()
```
> more concerns about bot

Bayesian ZOIB
---
```{r}
d <- df_survey_wp %>% 
  select(pid, order, privacy_bot, privacy_form) %>% 
  pivot_longer(cols = -c(pid, order),
               names_pattern = "privacy_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = value/100)

# f <- bf(
#   value_sc ~ method + (1|pid) + (method|order),
#   coi ~ method + (1|pid) + (method|order),
#   zoi ~ method + (1|pid) + (method|order),
#   phi ~ method + (1|pid) + (method|order)
# )
f <- bf(
  value_sc ~ method + (1|pid),
  coi ~ method + (1|pid),
  zoi ~ method + (1|pid),
  phi ~ method + (1|pid)
)

fit_privacy_zoib <- d %>%
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      control = list(adapt_delta = .90),
      file = "models/fit_privacy_zoib.rds",
      file_refit = "on_change"
  )

pp_check(fit_privacy_zoib)
summary(fit_privacy_zoib)


conditional_effects(fit_privacy_zoib)


mu_intercept <- as_draws_df(fit_privacy_zoib)$b_Intercept 
mu_method <- as_draws_df(fit_privacy_zoib)$b_methodform
coi_intercept <- as_draws_df(fit_privacy_zoib)$b_coi_Intercept
coi_method <- as_draws_df(fit_privacy_zoib)$b_coi_methodform
phi_intercept <- as_draws_df(fit_privacy_zoib)$b_phi_Intercept
phi_method <- as_draws_df(fit_privacy_zoib)$b_phi_methodform
zoi_intercept <- as_draws_df(fit_privacy_zoib)$b_zoi_Intercept
zoi_method <- as_draws_df(fit_privacy_zoib)$b_zoi_methodform

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) < 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) < 0"
)
hypothesis(fit_privacy_zoib, h, alpha = .05)
hypothesis(fit_privacy_zoib, h, alpha = .10)

```
> mu yes, coi yes (alpha = .10). more concerns about bot.


ZOIB between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, privacy_bot, privacy_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "privacy_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100)

f <- bf(
  value_sc ~ method,
  coi ~ method,
  zoi ~ method,
  phi ~ method
)

fit_privacy_bp_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      # control = list(adapt_delta = .90),
      file = "models/fit_privacy_zoib_between.rds",
      file_refit = "on_change"
  )
pp_check(fit_privacy_bp_zoib)
summary(fit_privacy_bp_zoib)

conditional_effects(fit_privacy_bp_zoib)

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) = 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) = 0",
  "phi" = "plogis(phi_Intercept + phi_methodform) - plogis(phi_Intercept) = 0",
  "zoi" = "plogis(zoi_Intercept + zoi_methodform) - plogis(zoi_Intercept) = 0"
)

hypothesis(fit_privacy_bp_zoib, h, alpha = .05)
hypothesis(fit_privacy_bp_zoib, h, alpha = .10)



```

Beta between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, privacy_bot, privacy_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "privacy_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100) %>% 
  mutate(value_sc = case_when(
    value_sc == 0 ~ 0.01,
    value_sc == 1 ~ 0.99,
    TRUE ~ value_sc
  )) %>% 
  mutate(method = factor(method, levels = c("form", "bot"))) 

f <- bf(
  value_sc ~ method,
  phi ~ method
)

fit_privacy_bp_beta <- d %>% 
  brm(f,
      data = .,
      family = Beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_privacy_beta_between.rds",
      file_refit = "on_change"
  )


pp_check(fit_privacy_bp_beta)
summary(fit_privacy_bp_beta)

h <- c(
  "mu" = "plogis(Intercept + methodbot) - plogis(Intercept) < 0"
)
hypothesis(fit_privacy_bp_beta, h, alpha = .05)
hypothesis(fit_privacy_bp_beta, h, alpha = .10)

```


Bayesian gaussian
---
```{r}
d <- df_survey_wp %>% 
  select(pid, privacy_bot, privacy_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "privacy_(.*)", 
               names_to = "method",
               values_to = "value")

hist(d$value)

fit_privacy_gaussian <- d %>%
  brm(value ~ method + (1|pid),
      data = .,
      family = gaussian(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_privacy_gaussian.rds",
      file_refit = "on_change"
  )

pp_check(fit_privacy_gaussian)
summary(fit_privacy_gaussian)
```



Recommend to friend
===

lmer
---
```{r}
d <- df_survey_wp %>% 
  select(pid, recommend_bot, recommend_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "recommend_(.*)", 
               names_to = "method",
               values_to = "value") 

d %>% 
  ggplot(aes(x = method, y = value)) +
  geom_point(position=position_jitter(.05)) +
  stat_summary(fun.data = "mean_cl_boot")

d %>% 
  lmer(value ~ method + (1|method), data = .) %>%
  tab_model()
```


Bayesian ZOIB
---
```{r}
d <- df_survey_wp %>% 
  select(pid, order, recommend_bot, recommend_form) %>% 
  pivot_longer(cols = -c(pid, order),
               names_pattern = "recommend_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = value/100)


# f <- bf(
#   value_sc ~ method + (1|pid) + (method|order),
#   coi ~ method + (1|pid) + (method|order),
#   zoi ~ method + (1|pid) + (method|order),
#   phi ~ method + (1|pid) + (method|order)
# )
f <- bf(
  value_sc ~ method + (1|pid),
  coi ~ method + (1|pid),
  zoi ~ method + (1|pid),
  phi ~ method + (1|pid)
)

fit_recommend_zoib <- d %>%
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      control = list(adapt_delta = .90),
      file = "models/fit_recommend_zoib.rds",
      file_refit = "on_change"
  )

pp_check(fit_recommend_zoib)
summary(fit_recommend_zoib)

conditional_effects(fit_recommend_zoib)
# d %>% 
#   ggplot(aes(x = method, y = value)) +
#   stat_summary(fun.data = "mean_cl_boot")


mu_intercept <- as_draws_df(fit_recommend_zoib)$b_Intercept 
mu_method <- as_draws_df(fit_recommend_zoib)$b_methodform
coi_intercept <- as_draws_df(fit_recommend_zoib)$b_coi_Intercept
coi_method <- as_draws_df(fit_recommend_zoib)$b_coi_methodform
phi_intercept <- as_draws_df(fit_recommend_zoib)$b_phi_Intercept
phi_method <- as_draws_df(fit_recommend_zoib)$b_phi_methodform
zoi_intercept <- as_draws_df(fit_recommend_zoib)$b_zoi_Intercept
zoi_method <- as_draws_df(fit_recommend_zoib)$b_zoi_methodform

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) < 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) < 0"
)
hypothesis(fit_recommend_zoib, h, alpha = .05)
hypothesis(fit_recommend_zoib, h, alpha = .10)

```
> mu yes, coi yes, 

```{r}
d <- df_survey_wp %>% 
  select(pid, order, recommend_bot, recommend_form) %>% 
  pivot_longer(cols = -c(pid, order),
               names_pattern = "recommend_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  mutate(value_sc = value/100)

d %>% 
  filter(value_sc == 0 | value_sc == 1) %>%
  group_by(method) %>% 
  summarize(
    pr = mean(value_sc)
  )

f <- bf(
  value_sc ~ method,
  coi ~ method,
  zoi ~ method,
  phi ~ method
)

fit_recommend_zoib_noRE <- brm(
  f,
  data = d,
  family = zero_one_inflated_beta(),
  cores = 4,
  chains = 4,
  iter = 5000,
  warmup = 1000,
  control = list(adapt_delta = .90),
  file = "models/fit_recommend_zoib_noRE.rds",
  file_refit = "on_change"
)


h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) < 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) < 0"
)
hypothesis(fit_recommend_zoib_noRE, h, alpha = .05)
hypothesis(fit_recommend_zoib_noRE, h, alpha = .10)


coi_intercept <- as_draws_df(fit_recommend_zoib_noRE)$b_coi_Intercept
coi_method <- as_draws_df(fit_recommend_zoib_noRE)$b_coi_methodform

mean(plogis(coi_intercept + coi_method) - plogis(coi_intercept))
```


ZOIB between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, recommend_bot, recommend_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "recommend_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100)

f <- bf(
  value_sc ~ method,
  coi ~ method,
  zoi ~ method,
  phi ~ method
)

fit_recommend_bp_zoib <- d %>% 
  brm(f,
      data = .,
      family = zero_one_inflated_beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      # control = list(adapt_delta = .90),
      file = "models/fit_recommend_zoib_between.rds",
      file_refit = "on_change"
  )

pp_check(fit_recommend_bp_zoib)
summary(fit_recommend_bp_zoib)

h <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) = 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) = 0",
  "phi" = "plogis(phi_Intercept + phi_methodform) - plogis(phi_Intercept) = 0",
  "zoi" = "plogis(zoi_Intercept + zoi_methodform) - plogis(zoi_Intercept) = 0"
)

hypothesis(fit_recommend_bp_zoib, h, alpha = .05)
hypothesis(fit_recommend_bp_zoib, h, alpha = .10)
```

Beta between
---
```{r}
d <- df_survey_bp %>% 
  select(pid, first_activity, recommend_bot, recommend_form) %>% 
  pivot_longer(cols = -c(pid, first_activity),
               names_pattern = "recommend_(.*)", 
               names_to = "method",
               values_to = "value") %>% 
  filter(first_activity == method) %>% 
  mutate(value_sc = value/100) %>% 
  mutate(value_sc = case_when(
    value_sc == 0 ~ 0.01,
    value_sc == 1 ~ 0.99,
    TRUE ~ value_sc
  )) %>% 
  mutate(method = factor(method, levels = c("form", "bot"))) 

f <- bf(
  value_sc ~ method,
  phi ~ method
)

fit_recommend_bp_beta <- d %>% 
  brm(f,
      data = .,
      family = Beta(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_recommend_beta_between.rds",
      file_refit = "on_change"
  )

pp_check(fit_recommend_bp_beta)
summary(fit_recommend_bp_beta)

h <- c(
  "mu" = "plogis(Intercept + methodbot) - plogis(Intercept) > 0"
)
hypothesis(fit_recommend_bp_beta, h, alpha = .05)
hypothesis(fit_recommend_bp_beta, h, alpha = .10)

```


Bayesian gaussian
---
```{r}


d <- df_survey_wp %>% 
  select(pid, recommend_bot, recommend_form) %>% 
  pivot_longer(cols = -pid, 
               names_pattern = "recommend_(.*)", 
               names_to = "method",
               values_to = "value")

fit_recommend_gaussian <- d %>%
  brm(value ~ method + (1|pid),
      data = .,
      family = gaussian(),
      cores = 4,
      chains = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_recommend_gaussian.rds",
      file_refit = "on_change"
  )

pp_check(fit_recommend_gaussian)
summary(fit_recommend_gaussian)

```


ZOIB table
===
```{r}
h_form_equal <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) = 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) = 0",
  "phi" = "plogis(phi_Intercept + phi_methodform) - plogis(phi_Intercept) = 0",
  "zoi" = "plogis(zoi_Intercept + zoi_methodform) - plogis(zoi_Intercept) = 0"
)

round_n <- 4

(h_articulate_zoib_90 <- hypothesis(fit_articulate_zoib, 
                                    h_form_equal, alpha=.10))
(h_difficult_zoib_90 <- hypothesis(fit_difficult_zoib,
                                   h_form_equal, alpha=.10))
(h_valuable_zoib_90 <- hypothesis(fit_valuable_zoib,
                                  h_form_equal, alpha=.10))
(h_feelingChange_zoib_90 <- hypothesis(fit_feelingChange_zoib, 
                                       h_form_equal, alpha=.10))
(h_recommend_zoib_90 <- hypothesis(fit_recommend_zoib, 
                                   h_form_equal, alpha=.10))
(h_acc_obj_zoib_90 <- hypothesis(fit_acc_obj_zoib, 
                                 h_form_equal, alpha=.10))
(h_acc_feel_zoib_90 <- hypothesis(fit_acc_feel_zoib, 
                                  h_form_equal, alpha=.10))
(h_otherUnderstand_zoib_90 <- hypothesis(fit_otherUnderstand_zoib, 
                                         h_form_equal, alpha=.10))
(h_privacy_zoib_90 <- hypothesis(fit_privacy_zoib, h_form_equal, alpha=.10))
(h_recommend_zoib_90 <- hypothesis(fit_recommend_zoib, h_form_equal, alpha=.10))


(h_articulate_zoib_95 <- hypothesis(fit_articulate_zoib,
                                    h_form_equal, alpha=.05))
(h_difficult_zoib_95 <- hypothesis(fit_difficult_zoib,
                                   h_form_equal, alpha=.05))
(h_valuable_zoib_95 <- hypothesis(fit_valuable_zoib, 
                                  h_form_equal, alpha=.05))
(h_feelingChange_zoib_95 <- hypothesis(fit_feelingChange_zoib, 
                                       h_form_equal, alpha=.05))
(h_recommend_zoib_95 <- hypothesis(fit_recommend_zoib, 
                                   h_form_equal, alpha=.05))
(h_acc_obj_zoib_95 <- hypothesis(fit_acc_obj_zoib,
                                 h_form_equal, alpha=.05))
(h_acc_feel_zoib_95 <- hypothesis(fit_acc_feel_zoib, 
                                  h_form_equal, alpha=.05))
(h_otherUnderstand_zoib_95 <- hypothesis(fit_otherUnderstand_zoib,
                                         h_form_equal, alpha=.05))
(h_privacy_zoib_95 <- hypothesis(fit_privacy_zoib, 
                                 h_form_equal, alpha=.05))
(h_recommend_zoib_95 <- hypothesis(fit_recommend_zoib, 
                                   h_form_equal, alpha=.05))

cri_articulate_mu_est <- round(h_articulate_zoib_90$hypothesis$Estimate[[1]], round_n)
cri_articulate_mu_95 <- paste0(
  "[",
  round(h_articulate_zoib_95$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_articulate_zoib_95$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_articulate_coi_est <- round(h_articulate_zoib_90$hypothesis$Estimate[[2]], round_n)
cri_articulate_coi_95 <- paste0(
  "[",
  round(h_articulate_zoib_95$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_articulate_zoib_95$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_articulate_phi_est <- round(h_articulate_zoib_90$hypothesis$Estimate[[3]], round_n)
cri_articulate_phi_95 <- paste0(
  "[",
  round(h_articulate_zoib_95$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_articulate_zoib_95$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_articulate_zoi_est <- round(h_articulate_zoib_90$hypothesis$Estimate[[4]], round_n)
cri_articulate_zoi_95 <- paste0(
  "[",
  round(h_articulate_zoib_95$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_articulate_zoib_95$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_difficult_mu_est <- round(h_difficult_zoib_90$hypothesis$Estimate[[1]], round_n)
cri_difficult_mu_95 <- paste0(
  "[",
  round(h_difficult_zoib_95$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_difficult_zoib_95$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_difficult_coi_est <- round(h_difficult_zoib_90$hypothesis$Estimate[[2]], round_n)
cri_difficult_coi_95 <- paste0(
  "[",
  round(h_difficult_zoib_95$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_difficult_zoib_95$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_difficult_phi_est <- round(h_difficult_zoib_90$hypothesis$Estimate[[3]], round_n)
cri_difficult_phi_95 <- paste0(
  "[",
  round(h_difficult_zoib_95$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_difficult_zoib_95$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_difficult_zoi_est <- round(h_difficult_zoib_90$hypothesis$Estimate[[4]], round_n)
cri_difficult_zoi_95 <- paste0(
  "[",
  round(h_difficult_zoib_95$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_difficult_zoib_95$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_valuable_mu_est <- round(h_valuable_zoib_90$hypothesis$Estimate[[1]], round_n)
cri_valuable_mu_95 <- paste0(
  "[",
  round(h_valuable_zoib_95$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_valuable_zoib_95$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_valuable_coi_est <- round(h_valuable_zoib_90$hypothesis$Estimate[[2]], round_n)
cri_valuable_coi_95 <- paste0(
  "[",
  round(h_valuable_zoib_95$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_valuable_zoib_95$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_valuable_phi_est <- round(h_valuable_zoib_90$hypothesis$Estimate[[3]], round_n)
cri_valuable_phi_95 <- paste0(
  "[",
  round(h_valuable_zoib_95$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_valuable_zoib_95$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_valuable_zoi_est <- round(h_valuable_zoib_90$hypothesis$Estimate[[4]], round_n)
cri_valuable_zoi_95 <- paste0(
  "[",
  round(h_valuable_zoib_95$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_valuable_zoib_95$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_feelingChange_mu_est <- round(h_feelingChange_zoib_90$hypothesis$Estimate[[1]], round_n)
cri_feelingChange_mu_95 <- paste0(
  "[",
  round(h_feelingChange_zoib_95$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_feelingChange_zoib_95$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_feelingChange_coi_est <- round(h_feelingChange_zoib_90$hypothesis$Estimate[[2]], round_n)
cri_feelingChange_coi_95 <- paste0(
  "[",
  round(h_feelingChange_zoib_95$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_feelingChange_zoib_95$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_feelingChange_phi_est <- round(h_feelingChange_zoib_90$hypothesis$Estimate[[3]], round_n)
cri_feelingChange_phi_95 <- paste0(
  "[",
  round(h_feelingChange_zoib_95$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_feelingChange_zoib_95$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_feelingChange_zoi_est <- round(h_feelingChange_zoib_90$hypothesis$Estimate[[4]], round_n)
cri_feelingChange_zoi_95 <- paste0(
  "[",
  round(h_feelingChange_zoib_95$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_feelingChange_zoib_95$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_recommend_mu_est <- round(h_recommend_zoib_90$hypothesis$Estimate[[1]], round_n)
cri_recommend_mu_95 <- paste0(
  "[",
  round(h_recommend_zoib_95$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_recommend_zoib_95$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_recommend_coi_est <- round(h_recommend_zoib_90$hypothesis$Estimate[[2]], round_n)
cri_recommend_coi_95 <- paste0(
  "[",
  round(h_recommend_zoib_95$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_recommend_zoib_95$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_recommend_phi_est <- round(h_recommend_zoib_90$hypothesis$Estimate[[3]], round_n)
cri_recommend_phi_95 <- paste0(
  "[",
  round(h_recommend_zoib_95$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_recommend_zoib_95$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_recommend_zoi_est <- round(h_recommend_zoib_90$hypothesis$Estimate[[4]], round_n)
cri_recommend_zoi_95 <- paste0(
  "[",
  round(h_recommend_zoib_95$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_recommend_zoib_95$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_acc_obj_mu_est <- round(h_acc_obj_zoib_90$hypothesis$Estimate[[1]], round_n)
cri_acc_obj_mu_95 <- paste0(
  "[",
  round(h_acc_obj_zoib_95$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_acc_obj_zoib_95$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_acc_obj_coi_est <- round(h_acc_obj_zoib_90$hypothesis$Estimate[[2]], round_n)
cri_acc_obj_coi_95 <- paste0(
  "[",
  round(h_acc_obj_zoib_95$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_acc_obj_zoib_95$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_acc_obj_phi_est <- round(h_acc_obj_zoib_90$hypothesis$Estimate[[3]], round_n)
cri_acc_obj_phi_95 <- paste0(
  "[",
  round(h_acc_obj_zoib_95$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_acc_obj_zoib_95$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_acc_obj_zoi_est <- round(h_acc_obj_zoib_90$hypothesis$Estimate[[4]], round_n)
cri_acc_obj_zoi_95 <- paste0(
  "[",
  round(h_acc_obj_zoib_95$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_acc_obj_zoib_95$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_acc_feel_mu_est <- round(h_acc_feel_zoib_90$hypothesis$Estimate[[1]], round_n)
cri_acc_feel_mu_95 <- paste0(
  "[",
  round(h_acc_feel_zoib_95$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_acc_feel_zoib_95$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_acc_feel_coi_est <- round(h_acc_feel_zoib_90$hypothesis$Estimate[[2]], round_n)
cri_acc_feel_coi_95 <- paste0(
  "[",
  round(h_acc_feel_zoib_95$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_acc_feel_zoib_95$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_acc_feel_phi_est <- round(h_acc_feel_zoib_90$hypothesis$Estimate[[3]], round_n)
cri_acc_feel_phi_95 <- paste0(
  "[",
  round(h_acc_feel_zoib_95$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_acc_feel_zoib_95$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_acc_feel_zoi_est <- round(h_acc_feel_zoib_90$hypothesis$Estimate[[4]], round_n)
cri_acc_feel_zoi_95 <- paste0(
  "[",
  round(h_acc_feel_zoib_95$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_acc_feel_zoib_95$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_otherUnderstand_mu_est <- round(h_otherUnderstand_zoib_90$hypothesis$Estimate[[1]], round_n)
cri_otherUnderstand_mu_95 <- paste0(
  "[",
  round(h_otherUnderstand_zoib_95$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_otherUnderstand_zoib_95$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_otherUnderstand_coi_est <- round(h_otherUnderstand_zoib_90$hypothesis$Estimate[[2]], round_n)
cri_otherUnderstand_coi_95 <- paste0(
  "[",
  round(h_otherUnderstand_zoib_95$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_otherUnderstand_zoib_95$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_otherUnderstand_phi_est <- round(h_otherUnderstand_zoib_90$hypothesis$Estimate[[3]], round_n)
cri_otherUnderstand_phi_95 <- paste0(
  "[",
  round(h_otherUnderstand_zoib_95$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_otherUnderstand_zoib_95$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_otherUnderstand_zoi_est <- round(h_otherUnderstand_zoib_90$hypothesis$Estimate[[4]], round_n)
cri_otherUnderstand_zoi_95 <- paste0(
  "[",
  round(h_otherUnderstand_zoib_95$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_otherUnderstand_zoib_95$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_privacy_mu_est <- round(h_privacy_zoib_90$hypothesis$Estimate[[1]], round_n)
cri_privacy_mu_95 <- paste0(
  "[",
  round(h_privacy_zoib_95$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_privacy_zoib_95$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_privacy_coi_est <- round(h_privacy_zoib_90$hypothesis$Estimate[[2]], round_n)
cri_privacy_coi_95 <- paste0(
  "[",
  round(h_privacy_zoib_95$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_privacy_zoib_95$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_privacy_phi_est <- round(h_privacy_zoib_90$hypothesis$Estimate[[3]], round_n)
cri_privacy_phi_95 <- paste0(
  "[",
  round(h_privacy_zoib_95$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_privacy_zoib_95$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_privacy_zoi_est <- round(h_privacy_zoib_90$hypothesis$Estimate[[4]], round_n)
cri_privacy_zoi_95 <- paste0(
  "[",
  round(h_privacy_zoib_95$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_privacy_zoib_95$hypothesis$CI.Upper[[4]], round_n),
  "]"
)




t <- tribble(
  ~model, ~mu, ~mu95, ~coi, ~coi95, ~phi, ~phi95, ~zoi, ~zoi95,
  "articulate", cri_articulate_mu_est, cri_articulate_mu_95, cri_articulate_coi_est, cri_articulate_coi_95, cri_articulate_phi_est, cri_articulate_phi_95, cri_articulate_zoi_est, cri_articulate_zoi_95,
  "difficult", cri_difficult_mu_est, cri_difficult_mu_95, cri_difficult_coi_est, cri_difficult_coi_95, cri_difficult_phi_est, cri_difficult_phi_95, cri_difficult_zoi_est, cri_difficult_zoi_95,
  "valuable", cri_valuable_mu_est, cri_valuable_mu_95, cri_valuable_coi_est, cri_valuable_coi_95, cri_valuable_phi_est, cri_valuable_phi_95, cri_valuable_zoi_est, cri_valuable_zoi_95,
  # "feelingChange", cri_feelingChange_mu_est, cri_feelingChange_mu_95, cri_feelingChange_coi_est, cri_feelingChange_coi_95, cri_feelingChange_phi_est, cri_feelingChange_phi_95, cri_feelingChange_zoi_est, cri_feelingChange_zoi_95,
  "recommend", cri_recommend_mu_est, cri_recommend_mu_95, cri_recommend_coi_est, cri_recommend_coi_95, cri_recommend_phi_est, cri_recommend_phi_95, cri_recommend_zoi_est, cri_recommend_zoi_95,
  "acc_obj", cri_acc_obj_mu_est, cri_acc_obj_mu_95, cri_acc_obj_coi_est, cri_acc_obj_coi_95, cri_acc_obj_phi_est, cri_acc_obj_phi_95, cri_acc_obj_zoi_est, cri_acc_obj_zoi_95,
  "acc_feel", cri_acc_feel_mu_est, cri_acc_feel_mu_95, cri_acc_feel_coi_est, cri_acc_feel_coi_95, cri_acc_feel_phi_est, cri_acc_feel_phi_95, cri_acc_feel_zoi_est, cri_acc_feel_zoi_95,
  "otherUnderstand", cri_otherUnderstand_mu_est, cri_otherUnderstand_mu_95, cri_otherUnderstand_coi_est, cri_otherUnderstand_coi_95, cri_otherUnderstand_phi_est, cri_otherUnderstand_phi_95, cri_otherUnderstand_zoi_est, cri_otherUnderstand_zoi_95,
  "privacy", cri_privacy_mu_est, cri_privacy_mu_95, cri_privacy_coi_est, cri_privacy_coi_95, cri_privacy_phi_est, cri_privacy_phi_95, cri_privacy_zoi_est, cri_privacy_zoi_95
  
)

view(t)
t %>% 
  write_csv("figures/zoib_table.csv")
# t <- tribble(
#   ~model, ~mu, ~mu95, ~mu90, ~coi, ~coi95, ~coi90, ~phi, ~phi95, ~phi90, ~zoi, ~zoi95, ~zoi90,
# )

fit_articulate_zoib
fit_difficult_zoib
fit_valuable_zoib
fit_feelingChange_zoib  # big problems
fit_recommend_zoib
fit_acc_obj_zoib
fit_acc_feel_zoib
fit_otherUnderstand_zoib
fit_privacy_zoib
fit_recommend_zoib

```


ZOIB table - between person
===
```{r}
h_form_equal <- c(
  "mu" = "plogis(Intercept + methodform) - plogis(Intercept) = 0",
  "coi" = "plogis(coi_Intercept + coi_methodform) - plogis(coi_Intercept) = 0",
  "phi" = "exp(phi_Intercept + phi_methodform) - exp(phi_Intercept) = 0",
  "zoi" = "plogis(zoi_Intercept + zoi_methodform) - plogis(zoi_Intercept) = 0"
)

hypothesis(fit_valuable_bp_zoib,
           "plogis(Intercept + methodform) - plogis(Intercept) < 0",
           alpha=.10)

round_n <- 4

(h_articulate_zoib_bp_90 <- hypothesis(fit_articulate_bp_zoib, 
                                       h_form_equal, alpha=.10))
(h_difficult_zoib_bp_90 <- hypothesis(fit_difficult_bp_zoib,
                                      h_form_equal, alpha=.10))
(h_valuable_zoib_bp_90 <- hypothesis(fit_valuable_bp_zoib,
                                     h_form_equal, alpha=.10))
# (h_feelingChange_zoib_bp_90 <- hypothesis(fit_feelingChange_bp_zoib, 
#                                           h_form_equal, alpha=.10))
(h_recommend_zoib_bp_90 <- hypothesis(fit_recommend_bp_zoib,
                                      h_form_equal, alpha=.10))
(h_acc_obj_zoib_bp_90 <- hypothesis(fit_acc_obj_bp_zoib,
                                    h_form_equal, alpha=.10))
(h_acc_feel_zoib_bp_90 <- hypothesis(fit_acc_feel_bp_zoib, 
                                     h_form_equal, alpha=.10))
(h_otherUnderstand_zoib_bp_90 <- hypothesis(fit_otherUnderstand_bp_zoib, 
                                            h_form_equal, alpha=.10))
(h_privacy_zoib_bp_90 <- hypothesis(fit_privacy_bp_zoib, h_form_equal, alpha=.10))
(h_recommend_zoib_bp_90 <- hypothesis(fit_recommend_bp_zoib, h_form_equal, alpha=.10))
(h_articulate_zoib_bp_95 <- hypothesis(fit_articulate_bp_zoib,
                                       h_form_equal, alpha=.05))
(h_difficult_zoib_bp_95 <- hypothesis(fit_difficult_bp_zoib,
                                      h_form_equal, alpha=.05))
(h_valuable_zoib_bp_95 <- hypothesis(fit_valuable_bp_zoib,
                                     h_form_equal, alpha=.05))
# (h_feelingChange_zoib_bp_95 <- hypothesis(fit_feelingChange_bp_zoib,
#                                           h_form_equal, alpha=.05))
(h_recommend_zoib_bp_95 <- hypothesis(fit_recommend_bp_zoib,
                                      h_form_equal, alpha=.05))
(h_acc_obj_zoib_bp_95 <- hypothesis(fit_acc_obj_bp_zoib,
                                    h_form_equal, alpha=.05))
(h_acc_feel_zoib_bp_95 <- hypothesis(fit_acc_feel_bp_zoib,
                                     h_form_equal, alpha=.05))
(h_otherUnderstand_zoib_bp_95 <- hypothesis(fit_otherUnderstand_bp_zoib,
                                            h_form_equal, alpha=.05))
(h_privacy_zoib_bp_95 <- hypothesis(fit_privacy_bp_zoib,
                                    h_form_equal, alpha=.05))
(h_recommend_zoib_bp_95 <- hypothesis(fit_recommend_bp_zoib,
                                      h_form_equal, alpha=.05))

cri_articulate_mu_est <- round(h_articulate_zoib_bp_90$hypothesis$Estimate[[1]], round_n)
cri_articulate_mu_90 <- paste0(
  "[",
  round(h_articulate_zoib_bp_90$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_articulate_zoib_bp_90$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_articulate_coi_est <- round(h_articulate_zoib_bp_90$hypothesis$Estimate[[2]], round_n)
cri_articulate_coi_90 <- paste0(
  "[",
  round(h_articulate_zoib_bp_90$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_articulate_zoib_bp_90$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_articulate_phi_est <- round(h_articulate_zoib_bp_90$hypothesis$Estimate[[3]], round_n)
cri_articulate_phi_90 <- paste0(
  "[",
  round(h_articulate_zoib_bp_90$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_articulate_zoib_bp_90$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_articulate_zoi_est <- round(h_articulate_zoib_bp_90$hypothesis$Estimate[[4]], round_n)
cri_articulate_zoi_90 <- paste0(
  "[",
  round(h_articulate_zoib_bp_90$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_articulate_zoib_bp_90$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_difficult_mu_est <- round(h_difficult_zoib_bp_90$hypothesis$Estimate[[1]], round_n)
cri_difficult_mu_90 <- paste0(
  "[",
  round(h_difficult_zoib_bp_90$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_difficult_zoib_bp_90$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_difficult_coi_est <- round(h_difficult_zoib_bp_90$hypothesis$Estimate[[2]], round_n)
cri_difficult_coi_90 <- paste0(
  "[",
  round(h_difficult_zoib_bp_90$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_difficult_zoib_bp_90$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_difficult_phi_est <- round(h_difficult_zoib_bp_90$hypothesis$Estimate[[3]], round_n)
cri_difficult_phi_90 <- paste0(
  "[",
  round(h_difficult_zoib_bp_90$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_difficult_zoib_bp_90$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_difficult_zoi_est <- round(h_difficult_zoib_bp_90$hypothesis$Estimate[[4]], round_n)
cri_difficult_zoi_90 <- paste0(
  "[",
  round(h_difficult_zoib_bp_90$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_difficult_zoib_bp_90$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_valuable_mu_est <- round(h_valuable_zoib_bp_90$hypothesis$Estimate[[1]], round_n)
cri_valuable_mu_90 <- paste0(
  "[",
  round(h_valuable_zoib_bp_90$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_valuable_zoib_bp_90$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_valuable_coi_est <- round(h_valuable_zoib_bp_90$hypothesis$Estimate[[2]], round_n)
cri_valuable_coi_90 <- paste0(
  "[",
  round(h_valuable_zoib_bp_90$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_valuable_zoib_bp_90$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_valuable_phi_est <- round(h_valuable_zoib_bp_90$hypothesis$Estimate[[3]], round_n)
cri_valuable_phi_90 <- paste0(
  "[",
  round(h_valuable_zoib_bp_90$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_valuable_zoib_bp_90$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_valuable_zoi_est <- round(h_valuable_zoib_bp_90$hypothesis$Estimate[[4]], round_n)
cri_valuable_zoi_90 <- paste0(
  "[",
  round(h_valuable_zoib_bp_90$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_valuable_zoib_bp_90$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

# cri_feelingChange_mu_est <- round(h_feelingChange_zoib_bp_90$hypothesis$Estimate[[1]], round_n)
# cri_feelingChange_mu_90 <- paste0(
#   "[",
#   round(h_feelingChange_zoib_bp_90$hypothesis$CI.Lower[[1]], round_n),
#   ", ",
#   round(h_feelingChange_zoib_bp_90$hypothesis$CI.Upper[[1]], round_n),
#   "]"
#   )
# cri_feelingChange_coi_est <- round(h_feelingChange_zoib_bp_90$hypothesis$Estimate[[2]], round_n)
# cri_feelingChange_coi_90 <- paste0(
#   "[",
#   round(h_feelingChange_zoib_bp_90$hypothesis$CI.Lower[[2]], round_n),
#   ", ",
#   round(h_feelingChange_zoib_bp_90$hypothesis$CI.Upper[[2]], round_n),
#   "]"
#   )
# cri_feelingChange_phi_est <- round(h_feelingChange_zoib_bp_90$hypothesis$Estimate[[3]], round_n)
# cri_feelingChange_phi_90 <- paste0(
#   "[",
#   round(h_feelingChange_zoib_bp_90$hypothesis$CI.Lower[[3]], round_n),
#   ", ",
#   round(h_feelingChange_zoib_bp_90$hypothesis$CI.Upper[[3]], round_n),
#   "]"
#   )
# cri_feelingChange_zoi_est <- round(h_feelingChange_zoib_bp_90$hypothesis$Estimate[[4]], round_n)
# cri_feelingChange_zoi_90 <- paste0(
#   "[",
#   round(h_feelingChange_zoib_bp_90$hypothesis$CI.Lower[[4]], round_n),
#   ", ",
#   round(h_feelingChange_zoib_bp_90$hypothesis$CI.Upper[[4]], round_n),
#   "]"
#   )

cri_recommend_mu_est <- round(h_recommend_zoib_bp_90$hypothesis$Estimate[[1]], round_n)
cri_recommend_mu_90 <- paste0(
  "[",
  round(h_recommend_zoib_bp_90$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_recommend_zoib_bp_90$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_recommend_coi_est <- round(h_recommend_zoib_bp_90$hypothesis$Estimate[[2]], round_n)
cri_recommend_coi_90 <- paste0(
  "[",
  round(h_recommend_zoib_bp_90$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_recommend_zoib_bp_90$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_recommend_phi_est <- round(h_recommend_zoib_bp_90$hypothesis$Estimate[[3]], round_n)
cri_recommend_phi_90 <- paste0(
  "[",
  round(h_recommend_zoib_bp_90$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_recommend_zoib_bp_90$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_recommend_zoi_est <- round(h_recommend_zoib_bp_90$hypothesis$Estimate[[4]], round_n)
cri_recommend_zoi_90 <- paste0(
  "[",
  round(h_recommend_zoib_bp_90$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_recommend_zoib_bp_90$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_acc_obj_mu_est <- round(h_acc_obj_zoib_bp_90$hypothesis$Estimate[[1]], round_n)
cri_acc_obj_mu_90 <- paste0(
  "[",
  round(h_acc_obj_zoib_bp_90$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_acc_obj_zoib_bp_90$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_acc_obj_coi_est <- round(h_acc_obj_zoib_bp_90$hypothesis$Estimate[[2]], round_n)
cri_acc_obj_coi_90 <- paste0(
  "[",
  round(h_acc_obj_zoib_bp_90$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_acc_obj_zoib_bp_90$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_acc_obj_phi_est <- round(h_acc_obj_zoib_bp_90$hypothesis$Estimate[[3]], round_n)

cri_acc_obj_phi_90 <- paste0(
  "[",
  round(h_acc_obj_zoib_bp_90$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_acc_obj_zoib_bp_90$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_acc_obj_zoi_est <- round(h_acc_obj_zoib_bp_90$hypothesis$Estimate[[4]], round_n)
cri_acc_obj_zoi_90 <- paste0(
  "[",
  round(h_acc_obj_zoib_bp_90$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_acc_obj_zoib_bp_90$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_acc_feel_mu_est <- round(h_acc_feel_zoib_bp_90$hypothesis$Estimate[[1]], round_n)
cri_acc_feel_mu_90 <- paste0(
  "[",
  round(h_acc_feel_zoib_bp_90$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_acc_feel_zoib_bp_90$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_acc_feel_coi_est <- round(h_acc_feel_zoib_bp_90$hypothesis$Estimate[[2]], round_n)
cri_acc_feel_coi_90 <- paste0(
  "[",
  round(h_acc_feel_zoib_bp_90$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_acc_feel_zoib_bp_90$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_acc_feel_phi_est <- round(h_acc_feel_zoib_bp_90$hypothesis$Estimate[[3]], round_n)
cri_acc_feel_phi_90 <- paste0(
  "[",
  round(h_acc_feel_zoib_bp_90$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_acc_feel_zoib_bp_90$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_acc_feel_zoi_est <- round(h_acc_feel_zoib_bp_90$hypothesis$Estimate[[4]], round_n)
cri_acc_feel_zoi_90 <- paste0(
  "[",
  round(h_acc_feel_zoib_bp_90$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_acc_feel_zoib_bp_90$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_otherUnderstand_mu_est <- round(h_otherUnderstand_zoib_bp_90$hypothesis$Estimate[[1]], round_n)
cri_otherUnderstand_mu_90 <- paste0(
  "[",
  round(h_otherUnderstand_zoib_bp_90$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_otherUnderstand_zoib_bp_90$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_otherUnderstand_coi_est <- round(h_otherUnderstand_zoib_bp_90$hypothesis$Estimate[[2]], round_n)
cri_otherUnderstand_coi_90 <- paste0(
  "[",
  round(h_otherUnderstand_zoib_bp_90$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_otherUnderstand_zoib_bp_90$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_otherUnderstand_phi_est <- round(h_otherUnderstand_zoib_bp_90$hypothesis$Estimate[[3]], round_n)
cri_otherUnderstand_phi_90 <- paste0(
  "[",
  round(h_otherUnderstand_zoib_bp_90$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_otherUnderstand_zoib_bp_90$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_otherUnderstand_zoi_est <- round(h_otherUnderstand_zoib_bp_90$hypothesis$Estimate[[4]], round_n)
cri_otherUnderstand_zoi_90 <- paste0(
  "[",
  round(h_otherUnderstand_zoib_bp_90$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_otherUnderstand_zoib_bp_90$hypothesis$CI.Upper[[4]], round_n),
  "]"
)

cri_privacy_mu_est <- round(h_privacy_zoib_bp_90$hypothesis$Estimate[[1]], round_n)
cri_privacy_mu_90 <- paste0(
  "[",
  round(h_privacy_zoib_bp_90$hypothesis$CI.Lower[[1]], round_n),
  ", ",
  round(h_privacy_zoib_bp_90$hypothesis$CI.Upper[[1]], round_n),
  "]"
)
cri_privacy_coi_est <- round(h_privacy_zoib_bp_90$hypothesis$Estimate[[2]], round_n)
cri_privacy_coi_90 <- paste0(
  "[",
  round(h_privacy_zoib_bp_90$hypothesis$CI.Lower[[2]], round_n),
  ", ",
  round(h_privacy_zoib_bp_90$hypothesis$CI.Upper[[2]], round_n),
  "]"
)
cri_privacy_phi_est <- round(h_privacy_zoib_bp_90$hypothesis$Estimate[[3]], round_n)
cri_privacy_phi_90 <- paste0(
  "[",
  round(h_privacy_zoib_bp_90$hypothesis$CI.Lower[[3]], round_n),
  ", ",
  round(h_privacy_zoib_bp_90$hypothesis$CI.Upper[[3]], round_n),
  "]"
)
cri_privacy_zoi_est <- round(h_privacy_zoib_bp_90$hypothesis$Estimate[[4]], round_n)
cri_privacy_zoi_90 <- paste0(
  "[",
  round(h_privacy_zoib_bp_90$hypothesis$CI.Lower[[4]], round_n),
  ", ",
  round(h_privacy_zoib_bp_90$hypothesis$CI.Upper[[4]], round_n),
  "]"
)


t <- tribble(
  ~model, ~mu, ~mu90, ~coi, ~coi90, ~phi, ~phi90, ~zoi, ~zoi90,
  "articulate", cri_articulate_mu_est, cri_articulate_mu_90, cri_articulate_coi_est, cri_articulate_coi_90, cri_articulate_phi_est, cri_articulate_phi_90, cri_articulate_zoi_est, cri_articulate_zoi_90,
  "difficult", cri_difficult_mu_est, cri_difficult_mu_90, cri_difficult_coi_est, cri_difficult_coi_90, cri_difficult_phi_est, cri_difficult_phi_90, cri_difficult_zoi_est, cri_difficult_zoi_90,
  "valuable", cri_valuable_mu_est, cri_valuable_mu_90, cri_valuable_coi_est, cri_valuable_coi_90, cri_valuable_phi_est, cri_valuable_phi_90, cri_valuable_zoi_est, cri_valuable_zoi_90,
  # "feelingChange", cri_feelingChange_mu_est, cri_feelingChange_mu_90, cri_feelingChange_coi_est, cri_feelingChange_coi_90, cri_feelingChange_phi_est, cri_feelingChange_phi_90, cri_feelingChange_zoi_est, cri_feelingChange_zoi_90,
  "recommend", cri_recommend_mu_est, cri_recommend_mu_90, cri_recommend_coi_est, cri_recommend_coi_90, cri_recommend_phi_est, cri_recommend_phi_90, cri_recommend_zoi_est, cri_recommend_zoi_90,
  "acc_obj", cri_acc_obj_mu_est, cri_acc_obj_mu_90, cri_acc_obj_coi_est, cri_acc_obj_coi_90, cri_acc_obj_phi_est, cri_acc_obj_phi_90, cri_acc_obj_zoi_est, cri_acc_obj_zoi_90,
  "acc_feel", cri_acc_feel_mu_est, cri_acc_feel_mu_90, cri_acc_feel_coi_est, cri_acc_feel_coi_90, cri_acc_feel_phi_est, cri_acc_feel_phi_90, cri_acc_feel_zoi_est, cri_acc_feel_zoi_90,
  "otherUnderstand", cri_otherUnderstand_mu_est, cri_otherUnderstand_mu_90, cri_otherUnderstand_coi_est, cri_otherUnderstand_coi_90, cri_otherUnderstand_phi_est, cri_otherUnderstand_phi_90, cri_otherUnderstand_zoi_est, cri_otherUnderstand_zoi_90,
  "privacy", cri_privacy_mu_est, cri_privacy_mu_90, cri_privacy_coi_est, cri_privacy_coi_90, cri_privacy_phi_est, cri_privacy_phi_90, cri_privacy_zoi_est, cri_privacy_zoi_90
)

view(t)

t %>% 
  write_csv("~/Downloads/zoib_table_bp.csv")
```


Beta table
===
```{r}
h_form_lower <- c(
  "mu" = "plogis(Intercept + methodbot) - plogis(Intercept) < 0"
)
h_form_higher <- c(
  "mu" = "plogis(Intercept + methodbot) - plogis(Intercept) > 0"
)
round_n <- 2
format_ci <- function(h, digits=round_n, h_idx=1) {
  paste0(
    "[",
    formatC(h$hypothesis$CI.Lower[[h_idx]]*100, digits=digits, format="f"),
    ", ",
    formatC(h$hypothesis$CI.Upper[[h_idx]]*100, digits=digits, format="f"),
    "]"
  )
}

(h_articulate_bp_95 <- hypothesis(fit_articulate_bp_beta, h_form_lower, alpha=.05))
(h_difficult_bp_95 <- hypothesis(fit_difficult_bp_beta, h_form_higher, alpha=.05))
(h_valuable_bp_95 <- hypothesis(fit_valuable_bp_beta, h_form_lower, alpha=.05))
# (h_feelingChange_bp_95 <- hypothesis(fit_feelingChange_bp_beta, h_form_lower, alpha=.05))
(h_recommend_bp_95 <- hypothesis(fit_recommend_bp_beta, h_form_lower, alpha=.05))
(h_acc_obj_bp_95 <- hypothesis(fit_acc_obj_bp_beta, h_form_lower, alpha=.05))
(h_acc_feel_bp_95 <- hypothesis(fit_acc_feel_bp_beta, h_form_lower, alpha=.05))
(h_otherUnderstand_bp_95 <- hypothesis(fit_otherUnderstand_bp_beta, h_form_lower, alpha=.05))
(h_privacy_bp_95 <- hypothesis(fit_privacy_bp_beta, h_form_higher, alpha=.05))

t <- tribble(
  ~model, ~mu, ~mu95,
  "articulate", h_articulate_bp_95$hypothesis$Estimate[[1]]*100, format_ci(h_articulate_bp_95),
  "difficult", h_difficult_bp_95$hypothesis$Estimate[[1]]*100, format_ci(h_difficult_bp_95),
  "valuable", h_valuable_bp_95$hypothesis$Estimate[[1]]*100, format_ci(h_valuable_bp_95),
  # "feelingChange", h_feelingChange_bp_95$hypothesis$Estimate[[1]], format_ci(h_feelingChange_bp_95),
  "recommend", h_recommend_bp_95$hypothesis$Estimate[[1]]*100, format_ci(h_recommend_bp_95),
  "acc_obj", h_acc_obj_bp_95$hypothesis$Estimate[[1]]*100, format_ci(h_acc_obj_bp_95),
  "acc_feel", h_acc_feel_bp_95$hypothesis$Estimate[[1]]*100, format_ci(h_acc_feel_bp_95),
  "otherUnderstand", h_otherUnderstand_bp_95$hypothesis$Estimate[[1]]*100, format_ci(h_otherUnderstand_bp_95),
  "privacy", h_privacy_bp_95$hypothesis$Estimate[[1]]*100, format_ci(h_privacy_bp_95)
) %>% 
  mutate(mu = formatC(mu, digits=round_n, format="f"))

view(t)
t %>% 
  write_csv("~/Downloads/beta_table_bp.csv")
```


Beta model figure
===
```{r}
form_articulate = plogis(as_draws_df(fit_articulate_bp_beta)$b_Intercept)
bot_articulate = plogis(as_draws_df(fit_articulate_bp_beta)$b_Intercept + as_draws_df(fit_articulate_bp_beta)$b_methodbot)

form_difficult = plogis(as_draws_df(fit_difficult_bp_beta)$b_Intercept)
bot_difficult = plogis(as_draws_df(fit_difficult_bp_beta)$b_Intercept + as_draws_df(fit_difficult_bp_beta)$b_methodbot)

form_valuable = plogis(as_draws_df(fit_valuable_bp_beta)$b_Intercept)
bot_valuable = plogis(as_draws_df(fit_valuable_bp_beta)$b_Intercept + as_draws_df(fit_valuable_bp_beta)$b_methodbot)

form_recommend = plogis(as_draws_df(fit_recommend_bp_beta)$b_Intercept)
bot_recommend = plogis(as_draws_df(fit_recommend_bp_beta)$b_Intercept + as_draws_df(fit_recommend_bp_beta)$b_methodbot)

form_acc_obj = plogis(as_draws_df(fit_acc_obj_bp_beta)$b_Intercept)
bot_acc_obj = plogis(as_draws_df(fit_acc_obj_bp_beta)$b_Intercept + as_draws_df(fit_acc_obj_bp_beta)$b_methodbot)

form_acc_feel = plogis(as_draws_df(fit_acc_feel_bp_beta)$b_Intercept)
bot_acc_feel = plogis(as_draws_df(fit_acc_feel_bp_beta)$b_Intercept + as_draws_df(fit_acc_feel_bp_beta)$b_methodbot)

form_otherUnderstand = plogis(as_draws_df(fit_otherUnderstand_bp_beta)$b_Intercept)
bot_otherUnderstand = plogis(as_draws_df(fit_otherUnderstand_bp_beta)$b_Intercept + as_draws_df(fit_otherUnderstand_bp_beta)$b_methodbot)

form_privacy = plogis(as_draws_df(fit_privacy_bp_beta)$b_Intercept)
bot_privacy = plogis(as_draws_df(fit_privacy_bp_beta)$b_Intercept + as_draws_df(fit_privacy_bp_beta)$b_methodbot)

df_plot_form <- tribble(
  ~model, ~est, ~hdi_hi, ~hdi_lo,
  "articulate", median(form_articulate), hdi(form_articulate, .95)[[2]], hdi(form_articulate, .95)[[1]],
  "difficult", median(form_difficult), hdi(form_difficult, .95)[[2]], hdi(form_difficult, .95)[[1]],
  "valuable", median(form_valuable), hdi(form_valuable, .95)[[2]], hdi(form_valuable, .95)[[1]],
  "recommend", median(form_recommend), hdi(form_recommend, .95)[[2]], hdi(form_recommend, .95)[[1]],
  "acc_obj", median(form_acc_obj), hdi(form_acc_obj, .95)[[2]], hdi(form_acc_obj, .95)[[1]],
  "acc_feel", median(form_acc_feel), hdi(form_acc_feel, .95)[[2]], hdi(form_acc_feel, .95)[[1]],
  "otherUnderstand", median(form_otherUnderstand), hdi(form_otherUnderstand, .95)[[2]], hdi(form_otherUnderstand, .95)[[1]],
  "privacy", median(form_privacy), hdi(form_privacy, .95)[[2]], hdi(form_privacy, .95)[[1]]
)
df_plot_bot <- tribble(
  ~model, ~est, ~hdi_hi, ~hdi_lo,
  "articulate", median(bot_articulate), hdi(bot_articulate, .95)[[2]], hdi(bot_articulate, .95)[[1]],
  "difficult", median(bot_difficult), hdi(bot_difficult, .95)[[2]], hdi(bot_difficult, .95)[[1]],
  "valuable", median(bot_valuable), hdi(bot_valuable, .95)[[2]], hdi(bot_valuable, .95)[[1]],
  "recommend", median(bot_recommend), hdi(bot_recommend, .95)[[2]], hdi(bot_recommend, .95)[[1]],
  "acc_obj", median(bot_acc_obj), hdi(bot_acc_obj, .95)[[2]], hdi(bot_acc_obj, .95)[[1]],
  "acc_feel", median(bot_acc_feel), hdi(bot_acc_feel, .95)[[2]], hdi(bot_acc_feel, .95)[[1]],
  "otherUnderstand", median(bot_otherUnderstand), hdi(bot_otherUnderstand, .95)[[2]], hdi(bot_otherUnderstand, .95)[[1]],
  "privacy", median(bot_privacy), hdi(bot_privacy, .95)[[2]], hdi(bot_privacy, .95)[[1]]
)
df_plot <- bind_rows(df_plot_form %>% mutate(condition = "form"),
                     df_plot_bot %>% mutate(condition = "bot")) %>% 
  mutate(model = case_when(
    model == "articulate" ~ "Helpful in \narticulating",
    model == "difficult" ~ "Difficult to\n respond",
    model == "valuable" ~ "Valuable \nfor youth",
    model == "recommend" ~ "Would \nRecommend",
    model == "acc_obj" ~ "Accurate \ncapturing \nsituation",
    model == "acc_feel" ~ "Accurate \ncapturing\n feelings",
    model == "otherUnderstand" ~ "Others would \nunderstand \nexperience",
    model == "privacy" ~ "Privacy \nconcerns"
  )) %>% 
  mutate(model = fct_reorder(model, est, .desc=T)) 

df_plot %>% 
  ggplot(aes(x = model, y = est, ymin = hdi_lo, ymax = hdi_hi, color=condition)) +
  geom_pointrange(position = position_dodge(width = .5)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  # coord_flip() +
  theme_minimal() +
  theme(legend.position = "bottom") +
  labs(
    x = "",
    y = " of estimated beta distribution",
    fill = "Condition"
  ) +
  # multiply the y-axis by 100 but not percent format
  scale_y_continuous(labels = scales::number_format(scale = 1e2),
                     limits = c(0,1)) +
  # rotate x axis labels and make text bigger
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) 

ggsave("~/Downloads/beta_plot_bp.png", width=8, height=6, dpi=300, bg="white")
```




Ease of capturing what you wanted
===
```{r}

df_survey_bp %>% 
  ggplot(aes(x = easeCapture_compare)) + 
  geom_histogram()


df_survey_bp %>% 
  summarize(
    mean = mean(easeCapture_compare, na.rm = TRUE),
    sd = sd(easeCapture_compare, na.rm = TRUE),
    n = n(),
    pr_bot_higher = mean(easeCapture_compare > 0, na.rm = TRUE),
  )
```
> bot much easier

Bayesian logit
---
```{r}
d <- df_survey_bp %>% 
  mutate(easeCapture_formEasier = case_when(
    easeCapture_compare > 0 ~ 0,
    easeCapture_compare < 0 ~ 1,
    TRUE ~ NA_real_
  ))

d$easeCapture_formEasier %>% table(useNA = "always")

fit_easeCapture_logistic <- d %>% 
  brm(easeCapture_formEasier ~ 1, 
      data = ., 
      family = bernoulli(link = "logit"),
      chains = 4,
      cores = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_easeCapture_logistic.rds",
      file_refit = "on_change"
  )
pp_check(fit_easeCapture_logistic)
summary(fit_easeCapture_logistic)

easeCapture_intercept <- as_draws_df(fit_easeCapture_logistic)$b_Intercept
mean(1/exp(easeCapture_intercept)) # inverse because I coded form as 1
hdi(1/exp(easeCapture_intercept), .95)
mean(plogis(easeCapture_intercept))

```

Appropriate for youth
===
```{r}
df_survey_bp %>% 
  ggplot(aes(x = forYouth_compare)) +
  geom_histogram()

df_survey_bp %>% 
  summarize(
    mean = mean(forYouth_compare, na.rm = TRUE),
    sd = sd(forYouth_compare, na.rm = TRUE),
    n = n(),
    pr_bot_higher = mean(forYouth_compare > 0, na.rm = TRUE),
  )
```
> bot more appropriate

Bayesian logit
---
```{r}
d <- df_survey_bp %>% 
  mutate(forYouth_formMoreAppropriate = case_when(
    forYouth_compare > 0 ~ 0,
    forYouth_compare < 0 ~ 1,
    TRUE ~ NA_real_
  ))

d$forYouth_formMoreAppropriate %>% table(useNA="always")

fit_forYouth_logistic <- d %>% 
  brm(forYouth_formMoreAppropriate ~ 1, 
      data = ., 
      family = bernoulli(link = "logit"),
      chains = 4,
      cores = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_forYouth_logistic.rds",
      file_refit = "on_change"
  )
pp_check(fit_forYouth_logistic)
summary(fit_forYouth_logistic)

forYouth_intercept <- as_draws_df(fit_forYouth_logistic)$b_Intercept
mean(1/exp(forYouth_intercept)) # inverse because I coded form as 1
hdi(1/exp(forYouth_intercept), .95)

```


Sense making
===
```{r}
df_survey_bp %>% 
  ggplot(aes(x = senseMaking_compare)) +
  geom_histogram()

df_survey_bp %>% 
  summarize(
    mean = mean(senseMaking_compare, na.rm = TRUE),
    sd = sd(senseMaking_compare, na.rm = TRUE),
    n = n(),
    pr_bot_higher = mean(senseMaking_compare > 0, na.rm = TRUE),
  )
```
> bot better


Bayesian logit
---
```{r}
d <- df_survey_bp %>% 
  mutate(senseMaking_formHigher = case_when(
    senseMaking_compare > 0 ~ 0,
    senseMaking_compare < 0 ~ 1,
    TRUE ~ NA_real_
  ))

d$senseMaking_formHigher %>% table(useNA="always")

fit_senseMaking_logistic <- d %>% 
  brm(senseMaking_formHigher ~ 1, 
      data = ., 
      family = bernoulli(link = "logit"),
      chains = 4,
      cores = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_senseMaking_logistic.rds",
      file_refit = "on_change"
  )
pp_check(fit_senseMaking_logistic)
summary(fit_senseMaking_logistic)

senseMaking_intercept <- as_draws_df(fit_senseMaking_logistic)$b_Intercept
mean(1/exp(senseMaking_intercept)) # inverse because I coded form as 1
hdi(1/exp(senseMaking_intercept), .95)

```

Captured your voice
===
```{r}

df_survey_bp %>% 
  ggplot(aes(x = captureVoice_compare)) +
  geom_histogram()

df_survey_bp %>% 
  summarize(
    mean = mean(captureVoice_compare, na.rm = TRUE),
    sd = sd(captureVoice_compare, na.rm = TRUE),
    n = n(),
    pr_bot_higher = mean(captureVoice_compare > 0, na.rm = TRUE),
  )
```
> bot captures voice

Bayesian logit
---
```{r}
d <- df_survey_bp %>% 
  mutate(captureVoice_formHigher = case_when(
    captureVoice_compare > 0 ~ 0,
    captureVoice_compare < 0 ~ 1,
    TRUE ~ NA_real_
  ))

d$captureVoice_formHigher %>% table(useNA="always")

fit_captureVoice_logistic <- d %>% 
  brm(captureVoice_formHigher ~ 1, 
      data = ., 
      family = bernoulli(link = "logit"),
      chains = 4,
      cores = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_captureVoice_logistic.rds",
      file_refit = "on_change"
  )

pp_check(fit_captureVoice_logistic)
summary(fit_captureVoice_logistic)

captureVoice_intercept <- as_draws_df(fit_captureVoice_logistic)$b_Intercept
mean(1/exp(captureVoice_intercept)) # inverse because I coded form as 1
hdi(1/exp(captureVoice_intercept), .95)

```



Helped address problem
===

```{r}

df_survey_bp %>% 
  ggplot(aes(x = probSolve_compare)) +
  geom_histogram()

hist(df_survey$probSolve_compare)

df_survey_bp %>% 
  summarize(
    mean = mean(probSolve_compare, na.rm = TRUE),
    sd = sd(probSolve_compare, na.rm = TRUE),
    n = n(),
    pr_bot_higher = mean(probSolve_compare > 0, na.rm = TRUE),
  )
```
> bot helped

Bayesian logit
---
```{r}
d <- df_survey_bp %>% 
  mutate(probSolve_formHigher = case_when(
    probSolve_compare > 0 ~ 0,
    probSolve_compare < 0 ~ 1,
    TRUE ~ NA_real_
  ))

d$probSolve_formHigher %>% table(useNA="always")

fit_probSolve_logistic <- d %>% 
  brm(probSolve_formHigher ~ 1, 
      data = ., 
      family = bernoulli(link = "logit"),
      chains = 4,
      cores = 4,
      iter = 5000,
      warmup = 1000,
      file = "models/fit_probSolve_logistic.rds",
      file_refit = "on_change"
  )

pp_check(fit_probSolve_logistic)
summary(fit_probSolve_logistic)

probSolve_intercept <- as_draws_df(fit_probSolve_logistic)$b_Intercept
mean(1/exp(probSolve_intercept)) # inverse because I coded form as 1
hdi(1/exp(probSolve_intercept), .95)

```


Logistic table
===
```{r}

round_n <- 2

or_easeCapture <- round(median(1/exp(easeCapture_intercept)), round_n)
or_forYouth <- round(median(1/exp(forYouth_intercept)), round_n)
or_senseMaking <- round(median(1/exp(senseMaking_intercept)), round_n)
or_captureVoice <- round(median(1/exp(captureVoice_intercept)), round_n)
or_probSolve <- round(median(1/exp(probSolve_intercept)), round_n)

cri_easeCapture <- paste0(
  "[",
  round(hdi(1/exp(easeCapture_intercept), .95)[1], round_n),
  ", ",
  round(hdi(1/exp(easeCapture_intercept), .95)[2], round_n),
  "]"
)
cri_forYouth <- paste0(
  "[",
  round(hdi(1/exp(forYouth_intercept), .95)[1], round_n),
  ", ",
  round(hdi(1/exp(forYouth_intercept), .95)[2], round_n),
  "]"
)
cri_senseMaking <- paste0(
  "[",
  round(hdi(1/exp(senseMaking_intercept), .95)[1], round_n),
  ", ",
  round(hdi(1/exp(senseMaking_intercept), .95)[2], round_n),
  "]"
)
cri_captureVoice <- paste0(
  "[",
  round(hdi(1/exp(captureVoice_intercept), .95)[1], round_n),
  ", ",
  round(hdi(1/exp(captureVoice_intercept), .95)[2], round_n),
  "]"
)
cri_probSolve <- paste0(
  "[",
  round(hdi(1/exp(probSolve_intercept), .95)[1], round_n),
  ", ",
  round(hdi(1/exp(probSolve_intercept), .95)[2], round_n),
  "]"
)

t <- tribble(
  ~model, ~or, ~ci,
  "easeCapture", or_easeCapture, cri_easeCapture,
  "forYouth", or_forYouth, cri_forYouth,
  "senseMaking", or_senseMaking, cri_senseMaking,
  "captureVoice", or_captureVoice, cri_captureVoice,
  "probSolve", or_probSolve, cri_probSolve
)


t %>% 
  write_csv("~/Downloads/logistic_table.csv")

```





Session Info
===
```{r}
sessionInfo()
```

